### 2024-10-21 chap_case_study/chap_case_study.tex
Final push for THESIS

Finally, this work includes updated values for some parameters compared to the work of \citet{limpens2021generating}. The main change concerns the cost and performance of private mobility vehicles, which is a key component in the European \cite{biresselioglu2018electric} and Belgian \cite{BFP_mob} energy transitions. Based on the work of the \citet{national2013transitions}, \citet{limpens2021generating} excessively favoured \gls{FC} car versus \gls{BEV}. In previous works \cite{limpens2021generating,rixhon2021role}, despite their lower efficiencies (\ie about 50\% less efficient), \gls{FC} cars had the bigger share of private mobility compared to battery electric vehicles(BEV) given the higher CAPEX (\ie up to 10\% more expensive) and limited range (\ie 24kWh battery) of the latter. In these works, the more limited potential to import electricity from abroad and to produce it locally via \gls{VRES} forced the model to electrify the low-temperature heat sector rather than the private mobility running on supposedly infinitely available renewable hydrogen. To align with other similar works on the modelling of whole-energy systems \cite{schnidrig2021modelling, EuropeanCommission2021}, the CAPEX and efficiency of fuel cell cars have been increased. Regarding \gls{BEV}, while the CAPEX has been kept unchanged, the efficiency and the battery capacity have been increased. As seen in the results, this change of data made \gls{BEV} often more competitive than its hydrogen-based equivalent.

>>>>

Finally, this work includes updated values for some parameters compared to the work of \citet{limpens2021generating}. The main change concerns the cost and performance of private mobility vehicles, which is a key component in the European \cite{biresselioglu2018electric} and Belgian \cite{BFP_mob} energy transitions. Based on the work of the \citet{national2013transitions}, \citet{limpens2021generating} excessively favoured \gls{FC} car versus \gls{BEV}. In previous works \cite{limpens2021generating,rixhon2021role}, despite their lower efficiencies (\ie about 50\% less efficient), \gls{FC} cars had the bigger share of private mobility compared to battery electric vehicles (BEV) given the higher CAPEX (\ie up to 10\% more expensive) and limited range (\ie 24kWh battery) of the latter. In these works, the more limited potential to import electricity from abroad and to produce it locally via \gls{VRES} forced the model to electrify the low-temperature heat sector rather than the private mobility running on supposedly infinitely available renewable hydrogen. To align with other similar works on the modelling of whole-energy systems \cite{schnidrig2021modelling, EuropeanCommission2021}, the CAPEX and efficiency of fuel cell cars have been increased. Regarding \gls{BEV}, while the CAPEX has been kept unchanged, the efficiency and the battery capacity have been increased. As seen in the results, this change of data made \gls{BEV} often more competitive than its hydrogen-based equivalent.
